\dnest~Manual

### 2016-01-19 doc/manual.tex
'code' in directory names

\subsection{Compiling}
Go into the {\tt code} directory and run {\tt make}. Everything should compile.
To
verify that the compilation was successful,
go into the {\tt Examples/SpikeSlab} directory
and see if an executable file called {\tt main} has been created. If you
execute this file, you should see a lot of output about ``levels'' and
``particles'' (see Figure~\ref{fig:output} for example output).
You will need to manually terminate this process by using
Control+C, or whatever works in your operating system. If you saw this output,
\dnest~was compiled successfully.\\

@@

To run the SpikeSlab example, go into the {\tt Examples/Spikeslab}
directory and execute {\tt main}. You should see some output that looks like
that shown in Figure~\ref{fig:output}.
Note that you must terminate the process manually by pressing Ctrl+C
or in another way. If you do not terminate the process yourself, it will run
forever. There is no definite rule for how long you should run \dnest.
It depends on the difficulty of your problem, the number of posterior samples you
want, and the accuracy you want for the marginal likelihood.\\

@@

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine,
RJObject\_SineWaves, and RJObject\_GalaxyField.
It also contains an empty Template example (in the Templates/BasicModel
subdirectory) which you can use
to implement your own models.\\

@@

\subsection{Compiling and running your model}
Assuming you implemented your model in the Template directory
(Templates/BasicModel), there's not
much else for you to do. The file {\tt main.cpp} already contains all the code
you need to construct a sampler and execute it. If your model involves a data
set, you'll just need to make sure you load the dataset at the beginning
of the {\tt main()} function, before doing anything else.\\

@@

\subsection{Implementing a model using Julia}
Experimental support for models implemented in Julia is provided in the
Templates/JuliaModel directory. There's a HOWTO file in that directory
with instructions for how to use it.

>>>>

\subsection{Compiling}
Go into the {\tt code} directory and run {\tt make}. Everything should compile.
To
verify that the compilation was successful,
go into the code/Examples/SpikeSlab directory
and see if an executable file called {\tt main} has been created. If you
execute this file, you should see a lot of output about ``levels'' and
``particles'' (see Figure~\ref{fig:output} for example output).
You will need to manually terminate this process by using
Control+C, or whatever works in your operating system. If you saw this output,
\dnest~was compiled successfully.\\

@@

To run the SpikeSlab example, go into the code/Examples/Spikeslab
directory and execute {\tt main}. You should see some output that looks like
that shown in Figure~\ref{fig:output}.
Note that you must terminate the process manually by pressing Ctrl+C
or in another way. If you do not terminate the process yourself, it will run
forever. There is no definite rule for how long you should run \dnest.
It depends on the difficulty of your problem, the number of posterior samples you
want, and the accuracy you want for the marginal likelihood.\\

@@

\section{Implementing models}
\dnest~currently includes three example models: SpikeSlab, StraightLine,
RJObject\_SineWaves, and RJObject\_GalaxyField.
It also contains an empty Template example (in the code/Templates/BasicModel
subdirectory) which you can use
to implement your own models.\\

@@

\subsection{Compiling and running your model}
Assuming you implemented your model in the Template directory
(code/Templates/BasicModel), there's not
much else for you to do. The file {\tt main.cpp} already contains all the code
you need to construct a sampler and execute it. If your model involves a data
set, you'll just need to make sure you load the dataset at the beginning
of the {\tt main()} function, before doing anything else.\\

@@

\subsection{Implementing a model using Julia}
Experimental support for models implemented in Julia is provided in the
code/Templates/JuliaModel directory. There's a HOWTO file in that directory
with instructions for how to use it.
